A generalized definition of multidimensional item response theory parameters

### 2024-09-05 output/Main_text.Rmd
Corrects and updates abstract

---
title: "A generalized definition of multidimensional item response theory parameters"
output:
  officedown::rdocx_document:
    tables:
      style: APA_Like_style
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
abstract: |
  Modern measurement theory demands that Multidimensional Item Response Theory
  accurately represents covariate spaces with correlated dimensions and/or
  non-standard variances. As it is also used in applications in the
  non-cognitive domain, they also need to model negatively-keyed items
  accurately and interpretably. Henceforth we generalize the
  multidimensional discrimination [@reckase_discriminating_1991] and
  difficulty [@reckase_difficulty_1985] parameters to account for those two
  phenomena. We do so by applying Reckase's [-@reckase_difficulty_1985] method
  in a strictly algebraic sense to the Multidimensional 2-Parameter Logistic
  Model, represented in a latent space with an arbitrary basis, and
  then defining such basis to be a concrete geometrical representation of the
  phenomena we intend to measure. This results in three different versions of
  the multidimensional parameters: The original one, based on the item
  parameters solely, one that incorporates the covariance structure of the
  latent space, and a third one that uses the correlation structure instead.
  Following @ackerman_creating_1994, we also provide a geometrical
  representation based on these parameters, and provide applied examples to
  illustrate the pertinence of these generalized parameters to represent the
  measurement properties of the items accurately. We recommend using the
  version that uses the latent covariance structure for describing the
  properties of the parameters, and the one based on the correlation structure
  for graphical representation. Finally, we discuss the implications of this
  generalization for other multidimensional IRT models, and the parallels of our
  results in common factor model theory.
keywords: |
  Multidimensional IRT, 2-Parameter Logistic model,
  multidimensional item discrimination, multidimensional item difficulty,
  item vector representation, test space
bibliography: [../../www/Multidimensional-parameters-MCLM.bib, ../../www/packages.bib]
csl:          ../../www/apa-old-doi-prefix.csl
editor_options: 
  chunk_output_type: console
---

@@

library(knitr)
library(patchwork)
library(ggplot2)
library(rstudioapi)

ROOT_DIR <- getActiveProject()
DOC_DIR  <- getwd()

>>>>

---
title: "A generalized definition of multidimensional item response theory parameters"
output:
  officedown::rdocx_document:
    tables:
      style: APA_Like_style
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
abstract: |
  Modern measurement theory demands that
  Multidimensional Item Response Theory models accurately represent
  covariance spaces with correlated dimensions and/or non-standard variances.
  As they are applied in the non-cognitive domain as well,
  they also need to model negatively-keyed items accurately and interpretably.
  Henceforth we generalize the multidimensional discrimination
  [@reckase_discriminating_1991] and difficulty [@reckase_difficulty_1985]
  parameters to account for those two phenomena.
  We do so by applying Reckase's [-@reckase_difficulty_1985] method
  in a strictly algebraic sense to the Multidimensional 2-Parameter Logistic
  Model, represented in a latent space with an arbitrary basis, and
  then defining such basis to be a concrete geometrical representation of the
  phenomena we intend to measure. This results in three different versions of
  the multidimensional parameters: The original one, based on the item
  parameters solely, one that incorporates the covariance structure of the
  latent space, and a third one that uses the correlation structure instead.
  Importantly, we find there is a test space where
  the items should be properly represented, which must be differentiated from
  the latent space itself.
  Following @ackerman_creating_1994, we also provide a geometrical
  representation based on these parameters in the test space.
  We apply our results to examples from the literature
  to illustrate the pertinence of these generalized parameters to get an
  accurate representation of the measurement properties of the items.
  We recommend using the version that uses the latent covariance structure
  for describing the properties of the parameters,
  and the one based on the correlation structure for graphical representation.
  Finally, we discuss the implications of this generalization for
  other multidimensional IRT models
  and the parallels of our results in common factor model theory.
keywords: |
  Multidimensional IRT, 2-Parameter Logistic model,
  multidimensional item discrimination, multidimensional item difficulty,
  item vector representation, test space
bibliography: [../www/Multidimensional-parameters-MCLM.bib, ../www/packages.bib]
csl:          ../www/apa-old-doi-prefix.csl
editor_options: 
  chunk_output_type: console
---

@@

library(here)
library(knitr)
library(patchwork)
library(ggplot2)
library(rstudioapi)

ROOT_DIR <- here()
DOC_DIR  <- file.path(ROOT_DIR, "output")
